Report on a Safety Checker for Petri nets

### 2013-11-18 paper/workspace/main.tex
Updated paper
Updated main

    nc      = 2 - t1 - t2 + t3 + t4
    ^         ^   ^    ^    ^    ^
    |         |   |    |    |    |
    place nc  |   ------    ------
              |      |         |
              |      |       input transitions of nc
              |      |    
              |    output transitions of nc
              |
           initial number of tokens in nc

@@

  Input:
    (S, T, E, I) : Petri net
  Output:
    C : State constraints

@@

TODO: Write the code

@@

TODO: Write the code
\end{verbatim}

@@

  Subprocedure TrapConditions constructs trap conditions C_\theta corresponding to N and A.
  Subprocedure \Delta constructs constraint \delta corresponding to A_\theta.
\end{verbatim}
\begin{center}
\begin{tikzpicture}
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                               	$C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                    	$\delta:=\Delta(A_\theta)$\\
                                    	$C:=C \cup \{\delta\}$};
  \node[print, right=of satc] (yes) {YES};
  \node[print, right=of satctheta] (dontknow) {Don't know};
  \node[state, right=of yes] (end1) {END};
  \node[state, right=of dontknow] (end2) {END};

@@

* Property of constraint \delta: Constraint \delta refines the abstraction, i.e.
  1. A ^ \delta is unsat (\delta excludes A)
  2. N |= \delta is sat  (\delta is a property of N)
\end{verbatim}

@@

  - Trap conditions C_\theta:
    nc  => t1 /\ t2
    m1  => t1 /\ t2
    m2  => t1 /\ t2
    cs1 => t3
    cs2 => t4

    t1  => m2 \/ cs1
    t2  => m1 \/ cs2
    t3  => m1 \/ nc
    t4  => m2 \/ nc

    nc \/ m1 \/ m2

    ~cs1 /\ ~cs2

  - Assignment A_\theta:
    nc  = false
    m1  = true
    m2  = true
    cs1 = false
    cs2 = false

    t1  = true
    t2  = true
    t3  = true
    t4  = true

  - Constraint \delta:
    m1 + m2 >= 1
\end{verbatim}

\section{Benchmarks of \bfc}

>>>>

    nc      = 2 - t1 - t2 + t3 + t4
    ^         ^   ^    ^    ^    ^
    |         |   |    |    |    |
    |         |   ------    ------
    |         |      |         |
    |         |      |       # of tokens given to nc
    |         |      |    
    |         |    # of tokens taken from nc
    |         |
    |      initial number of tokens in nc
    |
    number of tokens in nc

@@

  Input:
    (S, T, E, M0) : Petri net
  Output:
    C : State constraints

@@

TODO: Unroll pseudocode?

@@

@@

  Subprocedure TrapConditions constructs trap conditions C_\theta corresponding to N and A.
  Subprocedure \Delta constructs refinement constraint \delta corresponding to A_\theta.
\end{verbatim}
\begin{center}
\begin{tikzpicture}
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                               	$C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                    	$\delta:=\Delta(A_\theta)$\\
                                    	$C:=C \cup \{\delta\}$};
  \node[print, right=of satc] (yes) {YES};
  \node[print, right=of satctheta] (dontknow) {Don't know};
  \node[state, right=of yes] (end1) {END};
  \node[state, right=of dontknow] (end2) {END};

@@

* Property of A_\theta: for each place s, A_\theta(s) iff s \in S

* Property of refinement constraint \delta: Constraint \delta refines the abstraction, i.e.
  1. A ^ \delta is unsat (\delta excludes A)
  2. N |= \delta is sat  (\delta is a property of N)
\end{verbatim}

@@

  - Trap conditions C_\theta:

    - Trap implications:

    cs1 => m1 \/ nc
    ^      ^     ^
    |      |     |
    |      |     nc \in S
    |      |
    |      m1 \in S
    |
    cs1 \in S

    cs2 => m2 \/ nc
    nc  => (m2 \/ cs1) /\ (m1 \/ cs2)
    m1  => (m2 \/ cs1) /\ (m1 \/ cs2)
    m2  => (m2 \/ cs1) /\ (m1 \/ cs2)

    - At least one of the intially marked places belongs to S:
    nc \/ m1 \/ m2

    - None of the marked places in A belongs to S:
    ~cs1 /\ ~cs2

  - Assignment A_\theta:
    nc  = false
    m1  = true
    m2  = true
    cs1 = false
    cs2 = false
\end{verbatim}

\newpage
\begin{verbatim}
  - Refinement constraint \delta:
    m1 + m2 >= 1
    ^    ^
    |    |
    ------
      |
      S = {m1, m2}, therefore \delta excludes assignment A in the next iteration

* Trap implication:

  place s \in S =>    /\       \    /
                     /  \       \  /     place p \in S
                    /    \       \/
                   t \in s*   p \in t*

  "if s is in trap S then for each output transition t at least one successor p is in trap S"

* Refinement constraint \delta:

  \Sigma s >= 1  
  A(s)

  "At least one place in S is always marked"

* Subprocedure TrapConditions:

  Input:
    (S, T, E, M0) : Petri net
    A             : Satisfying assignment for C \cup { ~P }
  Output:
    C_\theta      : Trap conditions

  TODO: Unroll pseudocode?

* Subprocedure \Delta:

  Input:
    A_\theta      : Satisfying assignment for C_\theta
  Output:
    \delta        : Refinement constraint \delta

\newpage
\section{Benchmarks of \bfc}
